PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-16 manuscript.tex
Modify manuscript.

\peaknet{} exhibits exceptional capabilities in autonomous detection of Bragg
peaks in diffraction images without requiring user input or intervention, such
as algorithmic parameter tuning or manual artifact scattering masking.  The
predictive performance of \peaknet{} in peak finding proves to be comparable to,
if not better than, manually fine-tuned \psocake{} with user-supplied masks.  An
integral feature of \peaknet{}, auto-masking, significantly enhances its ability
to autonomously identify and process artifact scattering patterns.  Moreover,
the efficiency of \peaknet{} is exemplified by its impressive runtime
performance, surpassesing commonly used peak finders like \psocake{} and RPF.
Parallel processing with GPU streaming can potentially improve the runtime
efficiency even further.  In conclusion, \peaknet{}  offers a robust, versatile,
and efficient solution that operates independently of user input, thereby
holding significant potential for optimizing crystallographic data processing at
high data rates.

>>>>

\peaknet{} exhibits exceptional capabilities in autonomous Bragg peaks finding
without requiring user input or intervention, such as algorithmic parameter
tuning or manual artifact scattering masking.  The predictive performance of
\peaknet{} in peak finding proves to be comparable to, if not better than,
manually fine-tuned \psocake{} with user-supplied masks.  An integral feature of
\peaknet{}, auto-masking, significantly enhances its ability to autonomously
identify and process artifact scattering patterns.  Moreover, the efficiency of
\peaknet{} is exemplified by its impressive runtime performance, surpassesing
commonly used peak finders like \psocake{} and RPF.  Parallel processing with
GPU streaming can potentially improve the runtime efficiency even further.  In
conclusion, \peaknet{}  offers a robust, versatile, and efficient solution that
operates independently of user input, thereby holding significant potential for
optimizing crystallographic data processing at high data rates.
